### 2021-06-23 Supplementary_Material/Supplementary_Material.Rmd
edits

#SELFING
selfing <- readRDS("Data/RData/selfing_phylo.rds")
#FLOWER NUMBER
flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
#INFLO WIDTH
inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
#FLOWER WIDTH
flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
#FLOWER LENGHT
flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
#STYLE LENGTH
style_n <- readRDS("Data/RData/style_n_phylo.rds")
#OVULE NUMBER
ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
#PLANT HEIGHT
plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
#POLLEN
pollen <- readRDS("Data/RData/pollen_phylo.rds")
#Nectar ul
nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")
#Nectar mg
nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
#Nectar concentration
nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")

#Select two decimals function
specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
#LABELS
label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar ($\\mu$l) per flower", "Nectar (mg) per flower", "Nectar concentration ($\\%$)","Pollen grains per flower")
#LAMBDA
lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_mg$lambda, nectar_con$lambda, pollen$lambda)
#P-VALUE
p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,
            nectar_mg$P,  nectar_con$P, pollen$P)

>>>>

#SELFING
selfing <- readRDS("Data/RData/selfing_phylo.rds")
#FLOWER NUMBER
flower_n <- readRDS("Data/RData/flower_n_phylo.rds")
#INFLO WIDTH
inflow_width <- readRDS("Data/RData/inflow_width_phylo.rds")
#FLOWER WIDTH
flower_width <- readRDS("Data/RData/flower_width_phylo.rds")
#FLOWER LENGHT
flower_length <- readRDS("Data/RData/flower_length_phylo.rds")
#STYLE LENGTH
style_n <- readRDS("Data/RData/style_n_phylo.rds")
#OVULE NUMBER
ovule_n <- readRDS("Data/RData/ovule_n_phylo.rds")
#PLANT HEIGHT
plant_height <- readRDS("Data/RData/plant_height_phylo.rds")
#POLLEN
pollen <- readRDS("Data/RData/pollen_phylo.rds")
#Nectar ul
nectar_ul <- readRDS("Data/RData/Nectar_ul_phylo.rds")

#Not included at the end
#Nectar mg
#nectar_mg <- readRDS("Data/RData/Nectar_mg_phylo.rds")
#Nectar concentration
nectar_con <- readRDS("Data/RData/Nectar_concentration_phylo.rds")

#Select two decimals function
specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))
#LABELS
label <- c("Autonomous selfing", "Flower number", "Inflorescence width" ,"Flower width", "Flower length", "Style length", "Ovule number", "Plant height", "Nectar per flower ($\\mu$l)", "Nectar concentration ($\\%$)","Pollen grains per flower")
#LAMBDA
lambda <- c(selfing$lambda , flower_n$lambda, inflow_width$lambda, flower_width$lambda, flower_length$lambda, style_n$lambda, ovule_n$lambda, plant_height$lambda, nectar_ul$lambda, nectar_con$lambda, pollen$lambda)
#P-VALUE
p_value <- c(selfing$P , flower_n$P, inflow_width$P,flower_width$P, flower_length$P, style_n$P, ovule_n$P, plant_height$P,nectar_ul$P,  nectar_con$P, pollen$P)
